InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-02-09 paper.tex
Change heading
Update paper.tex
change some newlines, some wordings and spellings

\begin{abstract}
With the current rapid developments in AI generative content, the world gets flooded continuously more with AI generated content and with every new model it gets harder to differ between AI and human generated content. This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g. to detect fake news. This arises the field of tricking AI content detectors to create unrecognized AI generated content to bypass the mentioned AI detectors on the one hand and on the other hand this field is sufficient to improve the existing AI content detectors for more reliability and stability. The following paper tries to evaluate some methods to fool different AI detectors on differently generated images and texts.
\end{abstract}

@@

As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.

This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer. Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.

The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.\cite{radford2019language} try to avoid this problem in a simple two step procedure: Firstly, a generative pre-training of a language model on a varying corpus of unlabeled text. Secondly, discriminative fine-tuning on every specific task.

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}

@@

\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month. They have two primary methods for checking if a text is AI written. Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work. One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected. So this method is more generator-specific. \cite{WinstonAI}

@@

We used the aforementioned models for generating and detecting texts and images. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. We used gaussian noice, because it can occure due to natural sources and it is the most common noise that affects images naturally. \cite{mohammed2016study}

@@

As for text processors, we evaluated three different methods of augmenting generated texts. The first approach was to replace every white-space in a given text by two white-spaces. The second approach was to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like hitting a wrong key, which is close to the right one. This results in typos often created by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case French) and re-translate it into english. As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.

@@

\section{Discussion}
To summarize the results we can say, that the combination between generators and evaluators plays a huge role in the results. In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig. \ref{fig:falcon} and after processing as well, which means that if that would not have been the case, we would have a perfect score here.

>>>>

\begin{abstract}
With the current rapid developments in AI generative content, the world gets flooded continuously with AI generated content and with every new model it gets harder to differ between AI and human generated content. This lead to the development of multiple approaches to detect non human-made content like images and texts, e.g. to detect fake news. This arises the field of tricking AI content detectors to create unrecognized AI generated content to bypass the mentioned AI detectors on the one hand and on the other hand this field is sufficient to improve the existing AI content detectors for more reliability and stability. The following paper tries to evaluate some methods to fool different AI detectors on differently generated images and texts.
\end{abstract}

@@

As the second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.
This is done in two steps: Firstly, The images get compressed in a $32 \times 32$ grid of image tokens to reduce the context size of the transformer. Secondly, BPE-encoded text tokens are concatenated with the image tokens to model a joint distribution over text and image tokens with the training of an autoregressive transformer.
The exact procedure how DALL-E models work proposed by Ramesh et. al is explained in their paper. \cite{ramesh2021zeroshot}

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.\cite{radford2019language} try to avoid this problem in a simple two step procedure: Firstly, a generative pre-training of a language model on a varying corpus of unlabeled text. Secondly, discriminative fine-tuning on every specific task.
To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}

@@

\textbf{Winston AI} is a commercial AI text detector. They describe two primary methods for checking if a text is written by an AI. Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work. One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected. So this method is more generator-specific. \cite{WinstonAI}

@@

We used some of the aforementioned models for generating and detecting texts and images. For generating we used Stable Diffusion, OpenDalle, GPT2 and Falcon-RW-1B. For detecting we used RoBERTa Base OpenAI Detector, RADAR-Vicuna-7B, AIorNOT and ai-image-det-resnet18. As for image processors, one was already given in the description of the "InformatiCup2024" \cite{InformatiCup}, the image noising using the Gaussian noise. Image noise is the random variation of brightness or color information in images produced by the sensor and circuitry of a scanner or digital camera. We used gaussian noice, because it can occure due to natural sources and it is the most common noise that affects images naturally. \cite{mohammed2016study}

@@

As for text processors, we evaluated three different methods of augmenting generated texts. The first approach was to replace every white-space in a given text by two white-spaces. The second approach was to add some typos to the texts. This has been implemented based on the nlpaug library, which is capable of simulating certain typos as if they were made on a keyboard by a human. The typos include mistakes, like hitting a wrong key, which is close to the right one. This results in typos often created by humans. The last approach is a translator, which has been used to translate the given text into a certain language (in this case french) and re-translate it into english. As translators are not deterministic but aim to keep the semantic meaning, the resulting text should be semantically the same, but might have a different formulation.

@@

\section{Discussion}
To summarize the results we can say, that the combination between generators and evaluators plays a huge role in the results. In case of the text generators the difference seems minor, but for example the roberta base evaluator detected around ten falcon generated texts as human made in the middle case of fig. \ref{fig:falcon} before and after process, which means that if that would not have been the case, we would have a perfect score here.
